```latex
\documentclass[a4paper,10pt]{article}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{titlesec}

\geometry{left=1in, right=1in, top=1in, bottom=1in}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\bfseries}{}{0em}{}

\begin{document}

%-------------------- Title --------------------
\begin{center}
    \textbf{\huge Hassan Mikawi} \\
    \vspace{5pt}
    Software Engineer | Software Developer | Software Architect \\
    \vspace{5pt}
    Cairo, Egypt \\
    \href{mailto:hassan@ahram.org.eg}{hassan@ahram.org.eg} | \href{https://www.linkedin.com/in/mikawi}{LinkedIn} | \href{https://github.com/Hassan220022}{GitHub} | \href{https://mikawi.org}{Portfolio}
\end{center}

%-------------------- Professional Summary --------------------
\section*{Professional Summary}
Success is not achieved overnight, but is the result of accumulation over time. Passionate about software development and architecture with extensive experience in building robust applications. Committed to continuous learning and applying innovative solutions to complex problems.

%-------------------- Education --------------------
\section*{Education}
\textbf{Arab Academy for Science, Technology and Maritime Transport (AAST)}, Cairo, Egypt \\
Bachelor's degree in Computer Engineering \hfill \textit{Sep 2020 - Aug 2025} \\
GPA: 3.3/4.0 \\
Activities: AI Society, Innovation & Entrepreneurship Club, Professional Ping Pong Player

%-------------------- Experience --------------------
\section*{Experience}
\textbf{Software Engineer Intern} \\
Al-Ahram Establishment, Cairo, Egypt \hfill \textit{Sep 2024 - Dec 2024}
\begin{itemize}[leftmargin=0.15in]
    \item Developed Python scripts to automate data retrieval from Microsoft SQL Server.
    \item Built a fully functional agricultural website, handling both front-end and back-end development.
    \item Implemented security measures and managed site deployment on local servers.
    \item Optimized performance and traffic handling for stable operations.
\end{itemize}

\textbf{Intern} \\
Arab Organization for Industrialization (AOI), Cairo, Egypt \hfill \textit{Jun 2023 - Jul 2023}
\begin{itemize}[leftmargin=0.15in]
    \item Assisted in optimizing the hardware assembly line using lean manufacturing principles.
    \item Collaborated with engineering teams to refine design specifications.
\end{itemize}

%-------------------- Projects --------------------
\section*{Projects}
\textbf{Flex Programming Language (Graduation Project)} \hfill \textit{Jan 2024 - Apr 2025} \\
Developed a programming language with AI-assisted debugging, supporting multiple syntax styles (English, Arabic transliteration, and C-style). Built an online IDE and VSCode extensions for language support.

\textbf{Hyper Market Management System} \hfill \textit{Jun 2023} \\
Implemented a comprehensive market management system with Java and MySQL. Enhanced security with jBCrypt and packaged for easy installation.

%-------------------- Skills --------------------
\section*{Skills}
\begin{itemize}[leftmargin=0.15in]
    \item \textbf{Languages:} C/C++, C\#, Java, Python, JavaScript, Bash, SQL, Flutter
    \item \textbf{Operating Systems:} Windows, Linux, MacOS
    \item \textbf{Developer Tools:} Git, SSH, VS Code, Visual Studio, Docker
    \item \textbf{Methodologies:} Agile, Scrum, OOP, Functional Programming, DevOps, CI/CD, TDD
\end{itemize}

\end{document}
```